---
output: pdf_document
params:
  responsable: NA
  ID: NA
  verified: NA
  exposition: NA
  eplet_MM: NA
  DL23_table: NA
header-includes:
  - \usepackage{booktabs}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \definecolor{bluetitle}{HTML}{0071BC}
always_allow_html: true
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')
```


\begin{huge}
\textcolor{bluetitle}{DL2/3 report - Receptor `r params$ID`}
\end{huge}

Date of the report: `r Sys.Date()` \newline
Author: `r params$responsable` \newline\newline

**Parámetros del análisis**

```{r}
#Funcion que codifica la combinacion de mensajes que se imprimiran explicando los filtros usados para la seleccion de eplets
conditional_text <- function(verified, exposition) {
  verified_yes <- "For the evaluation of possible candidate specificities for delisting at the DL2/3 stage, only those eplets listed as verified by antibodies in the database https://www.epregistry.com.br/ have been taken into account."
  verified_no <- "For the evaluation of potential candidate specificities for delisting at the DL2/3 stage, only those eplets listed as **no** antibody-verified in the database https://www.epregistry.com.br/ have been taken into account."
  verified_all <- "For the evaluation of potential candidate specificities for delisting at the DL2/3 stage, all eplets have been taken into account regardless of whether they have been verified by antibodies or not, as listed in the database https://www.epregistry.com.br/."
  exposition_high <- "With regard to the level of exposure of each eplet in the associated HLA molecules, only those eplets with a high degree of exposure have been taken into account."
  exposition_intermediate <-  "With regard to the level of exposure of each eplet in the associated HLA molecules, only those eplets with an intermediate degree of exposure have been taken into account."
  exposition_low <- "With regard to the level of exposure of each eplet in the associated HLA molecules, only those eplets with a low degree of exposure have been taken into account."
  exposition_verylow <- "With regard to the level of exposure of each eplet in the associated HLA molecules, only those eplets with a very low degree of exposure have been taken into account."
  exposition_all <- "On the other hand, the level of exposure of the eplets on the HLA molecules with which they are associated **has not** been taken into account for their selection."

  mensaje_verified <- if (verified == "All") {
    verified_all
  } else if (verified == "Yes") {
    verified_yes
  } else if (verified == "No") {
    verified_no
  }

  mensaje_exposition <- if (exposition == "All") {
    exposition_all
  } else if (exposition == "High") {
    exposition_high
  } else if (exposition == "Intermediate") {
    exposition_intermediate
  } else if (exposition == "Low") {
    exposition_low
  } else if (exposition == "Very Low") {
    exposition_verylow
  }

  return(paste(mensaje_verified, mensaje_exposition))
}
```

`r conditional_text(params$verified, params$exposition)`


**Resultados DL2/3**

The set of prohibited eplets for a given recipient has been defined as the set of eplets present in previous donors that are not associated with any HLA allele of the recipient.
Based on the filtering criteria defined in the previous section, the complete list of prohibited eplets for the recipient **`r params$ID`** is as follows:

`r params$eplet_MM`


The specificities selected as candidates for DL2/3 phases are shown below. For each of them it is shown whether they contain any forbidden eplets for the **`r params$ID`** receptor, and based on this information, in which delisting phase they should be marked as allowed specificity:

```{r}
# Mostrar la tabla
kable(params$DL23_table, format = "latex", booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kableExtra::kable_styling(latex_options = "hold_position")
```

